### 2023-10-29 README.Rmd
updated createHOT - 231029

```{r}
CBC <- createHOT(
  data = CBC_lin, # data frame
  id = 1, # column index of the id
  none = 15, # column index of none alternative
  prod = 3, # number of alternatives in validation task (excluding none)
  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each attribute (for linear coded we specify value to be interpolated)
  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
  lin.p = 14, # column index of the linear coded variable
  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
  method = "CBC", # method
  varskeep = 17, # column index of variables that should be kept in the dataframe
  choice = 16 # column index of choice
)
```

>>>>

```{r}
CBC <- createHOT(
  data = CBC_lin, # data frame
  id = 1, # column index of the id
  none = 15, # column index of none alternative
  prod = 3, # number of alternatives in validation task (excluding none)
  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)), # column index of the attribute levels for each attribute (for linear coded we specify value to be interpolated)
  coding = c(0, 0, 1), # coding of the 3 attributes; 0 = part-worth, 1 = linear, 2 = piecewise
  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)), # actual values for the levels that should be interpolated
  lin.p = 14, # column index of the linear coded variable
  method = "CBC", # method
  varskeep = 17, # column index of variables that should be kept in the dataframe
  choice = 16 # column index of choice
)
```
